Building activity class prediction based on human activity data
========================================================

Here we try to build model to predict activity class based on measurment from wearable sensors like Jawbone and etc.
We use data from  http://groupware.les.inf.puc-rio.br/har. There are 19622 samples from 6 people in dataset. For classification we will use random forest algorithm.

Clean-up data set
==

First we will load and clean-up our test set.
```{r cache=TRUE}
TrainData<-read.csv("pml-training.csv")
summary(colSums(is.na(TrainData)))
summary(colSums(TrainData == ""))
```
We can see that number of NA's and empty strings in our data is equal for each column where ots presented, and it's more than 95% of data set. We can easy remove all that column

```{r cache=TRUE}
my_cols<-colSums(TrainData == "")
my_cols[is.na(my_cols)]<-19000
my_cols<-my_cols==0
CleanedTrainData<-TrainData[,my_cols]
```
Next we can remove timestamp, username, window-related info and number of experiment which will not have any usefull information
```{r }
CleanedTrainData<-CleanedTrainData[,8:60]
```

Fit Model
==
We will use random forest to fit our model with default parameters. 
We divide our date into train and test set (70% and 30% resp.) and fit the model
```{r}
library(randomForest)
set.seed(987)
splitInd<-rbinom(19622, 1, 0.3)==1
TrainSet<-CleanedTrainData[!splitInd,]
TestSet<-CleanedTrainData[splitInd,]
mymodel<-randomForest(classe~., data = TrainSet)
```
We get model, lets take a look
```{r}
mymodel$ntree
colMeans(mymodel$err.rate)
mymodel$confusion
summary(mymodel)
plot(mymodel)
```
We can see that classifier is pretty precise — error rate is smaller than 0.5%.

And now get error rate for test and training sets
```{r}
trainPrediction<-predict(mymodel, TrainSet)
testPrediction<-predict(mymodel, TestSet)
trainError = sum(trainPrediction!=TrainSet[,53])/length(trainPrediction)
testError = sum(testPrediction!=TestSet[,53])/length(testPrediction)
trainError
testError
```

We can see that error rate is also very small for test set, so classifier is pretty efficient at all.

Additional Insights
==
Probably we can clean up confusion matrix by include "user_name" in the prediction, but this will confuse model when we try to predict activity for new user. Also efficency of prediction for new user is not guarantied.

